Descriptive characteristics of Long COVID cohrots, matched

### 2022-11-17 characterisation/Code/Comparing_symptoms_matched.Rmd
update

load(here("data", "table1_data.Rdata"))
load(here("data", "table1_data_matched.Rdata"))

@@

```{r include=FALSE}
# variables for Table 1 
vars<-c(
        "age",
        "age_gr2",
        "gender",
        "trimester",
        "vaccination_status",
        "asthma",
        "autoimmune_disease",
        "copd",
        "dementia",
        "diabetes",
        "heart_disease",
        "cancer",
        "hypertension",
        "renal_impairment",
        "long_covid"
)

factor.vars<- c(
        "age_gr2",
        "gender",
        "trimester",
        "vaccination_status",
        "asthma",
        "autoimmune_disease",
        "copd",
        "dementia",
        "diabetes",
        "heart_disease",
        "cancer",
        "hypertension",
        "renal_impairment",
        "long_covid"
)

@@

# Baseline characteristics 
```{r}
table1.data<-rbind(  
# those without missing values
       table1_data_new_infections   %>%
        mutate(group = "1 COVID-19 infection"),
       table1_data_confirmed_infection  %>%
        mutate(group = "2 Confirmed infection"),
       table1_data_first_infection %>%
        mutate(group = "3 First infection"),
       table1_data_reinfections  %>%
        mutate(group = "4 Reinfections"),
        table1_data_tested_negative_earliest  %>%
        mutate(group = "5 Tested negative, earliest"),
       table1_data_tested_negative_all %>%
        mutate(group = "6 Tested negative, all "),
       table1_data_pcr_negative_earliest  %>%
        mutate(group = "7 PCR negative, earliest "),
       table1_data_pcr_negative_all  %>%
        mutate(group = "8 PCR negative, all ")) %>%
  filter(cohort_start_date >=full_testing_start_date)

summary.characteristics <-print(CreateTableOne(
  vars =  vars,
  factorVars = factor.vars,
  includeNA=T,
  data = table1.data,
  strata=c("group"),
  test = F), 
  showAllLevels=F,
  smd=F,
  nonnormal = vars, #all 
  noSpaces = TRUE,
  contDigits = 0,
  catDigits = 0,
  printToggle=FALSE)

@@

summary.characteristics_covid_negative <-print(svyCreateTableOne(
  vars =  vars,
  factorVars = factor.vars,
  includeNA=T,
  data = data,
  strata=c("name"),
  test = F), 
  showAllLevels=F,
  smd=T,
  nonnormal = vars, #all 
  noSpaces = TRUE,
  catDigits = 0,
  contDigits = 0,
  printToggle=FALSE)

@@

summary.characteristics.confirmed<-print(svyCreateTableOne(
  vars =  vars,
  factorVars = factor.vars,
  includeNA=T,
  data = data,
  strata=c("name"),
  test = F), 
  showAllLevels=F,
  smd=T,
  nonnormal = vars, #all 
  noSpaces = TRUE,
  contDigits = 0,
  catDigits = 0,
  printToggle=FALSE)

@@

```{r include=FALSE}
data <- m.first_infection_reinfections[[3]]

summary.characteristics.reinfections<-print(svyCreateTableOne(
  vars =  vars,
  factorVars = factor.vars,
  includeNA=T,
  data = data,
  strata=c("name"),
  test = F), 
  showAllLevels=F,
  smd=T,
  nonnormal = vars, #all 
  noSpaces = TRUE,
  contDigits = 0,
  catDigits = 0,
  printToggle=FALSE)

@@

summary.characteristics_symptoms <-print(svyCreateTableOne(
  vars =  vars,
  factorVars = factor.vars,
  includeNA=T,
  data = s.data,
  strata=c("name"),
  test = F), 
  showAllLevels=F,
  smd=T,
  nonnormal = vars, #all 
  noSpaces = TRUE,
  contDigits = 0,
   catDigits = 0,
  printToggle=FALSE)

@@

summary.characteristics_symptoms <-print(svyCreateTableOne(
  vars =  vars,
  factorVars = factor.vars,
  includeNA=T,
  data = s.data,
  strata=c("name"),
  test = F), 
  showAllLevels=F,
  smd=T,
  nonnormal = vars, #all 
  noSpaces = TRUE,
  contDigits = 0,
  catDigits = 0,
  printToggle=FALSE)
```

>>>>

load(here("data", "table1_data.Rdata"))
#load(here("data", "table1_data_matched.Rdata"))
load(here("data", "table1_data_matched_age_week.Rdata"))

nice.num<-function(x){
  prettyNum(x, big.mark=",", nsmall = 0, digits=0,scientific = FALSE)}
nice.num2<-function(x){
  prettyNum(x, big.mark=",", nsmall = 2, digits=2,scientific = FALSE)}

@@

```{r include=FALSE}
# variables for Table 1 
vars<-c(
        "age",
        "age_gr2",
        "gender",
        "trimester",
        "vaccination_status",
        "asthma",
        "autoimmune_disease",
        "copd",
        "dementia",
        "diabetes",
        "heart_disease",
        "cancer",
        "hypertension",
        "renal_impairment",
        "long_covid",
        "abdominal_pain",
        "allergy", 
        "altered_smell_taste",
        "anxiety" , 
        "blurred_vision" ,
        "chest_pain" ,
        "cognitive_dysfunction_brain_fog", 
        "cough" ,
        "depression" ,
        "dizziness" ,
        "dyspnea",
        "fatigue_malaise" ,
        "gastrointestinal_issues",
        "headache" ,
        "intermittent_fever",
        "joint_pain"  , 
        "memory_issues_v2" ,
        "menstrual_problems" ,
        "muscle_spams_pain",
        "neuralgia" , 
        "pins_sensation",  
        "sleep_disorder" ,
        "tachycardia" ,
        "tinnitus_hearing_problems", 
        "all_symp"
)

factor.vars<- c(
  "age_gr2",
        "gender",
        "trimester",
        "vaccination_status",
        "asthma",
        "autoimmune_disease",
        "copd",
        "dementia",
        "diabetes",
        "heart_disease",
        "cancer",
        "hypertension",
        "renal_impairment",
        "long_covid",
        "abdominal_pain",
        "allergy", 
        "altered_smell_taste",
        "anxiety" , 
        "blurred_vision" ,
        "chest_pain" ,
        "cognitive_dysfunction_brain_fog", 
        "cough" ,
        "depression" ,
        "dizziness" ,
        "dyspnea",
        "fatigue_malaise" ,
        "gastrointestinal_issues",
        "headache" ,
        "intermittent_fever",
        "joint_pain"  , 
        "memory_issues_v2" ,
        "menstrual_problems" ,
        "muscle_spams_pain",
        "neuralgia" , 
        "pins_sensation",  
        "sleep_disorder" ,
        "tachycardia" ,
        "tinnitus_hearing_problems", 
        "all_symp"
)

@@

# Baseline characteristics 
```{r}
table1.data<-rbind(  
# those without missing values
       table1_data_new_infections   %>%
        mutate(group = "1 COVID-19 infection"),
       table1_data_confirmed_infection  %>%
        mutate(group = "2 Confirmed infection"),
       table1_data_first_infection %>%
        mutate(group = "3 First infection"),
       table1_data_reinfections  %>%
        mutate(group = "4 Reinfections"),
        table1_data_tested_negative_earliest  %>%
        mutate(group = "5 Tested negative, earliest"),
       table1_data_tested_negative_all %>%
        mutate(group = "6 Tested negative, all"),
       table1_data_pcr_negative_earliest  %>%
        mutate(group = "7 PCR negative, earliest"),
       table1_data_pcr_negative_all  %>%
        mutate(group = "8 PCR negative, all")) %>%
  filter(cohort_start_date >=full_testing_start_date)

summary.characteristics <-print(CreateTableOne(
  vars =  vars,
  factorVars = factor.vars,
  includeNA=F,
  data = table1.data,
  strata=c("group"),
  test = F), 
  showAllLevels=F,
  smd=F,
  nonnormal = vars, #all 
  noSpaces = TRUE,
  printToggle=FALSE)

for(i in 1:8) {
# tidy up 
  cur_column <- summary.characteristics[, i]
  cur_column <- str_extract(cur_column, '[0-9.]+\\b') %>% 
                as.numeric() 
  cur_column <-nice.num(cur_column)
  # add back in
 summary.characteristics[, i] <- str_replace(string=summary.characteristics[, i],
                              pattern='[0-9.]+\\b', 
                              replacement=cur_column)    
}

@@

summary.characteristics_covid_negative <-print(svyCreateTableOne(
  vars =  vars,
  factorVars = factor.vars,
  includeNA=F,
  data = data,
  strata=c("name"),
  test = F), 
  showAllLevels=F,
  smd=T,
  nonnormal = vars, #all 
  noSpaces = TRUE,
  printToggle=FALSE)

for(i in 1:2) {
# tidy up 
  cur_column <- summary.characteristics_covid_negative[, i]
  cur_column <- str_extract(cur_column, '[0-9.]+\\b') %>% 
                as.numeric() 
  cur_column <-nice.num(cur_column)
  # add back in
 summary.characteristics_covid_negative[, i] <- str_replace(string=summary.characteristics_covid_negative[, i],
                              pattern='[0-9.]+\\b', 
                              replacement=cur_column)    
}

@@

summary.characteristics.confirmed<-print(svyCreateTableOne(
  vars =  vars,
  factorVars = factor.vars,
  includeNA=F,
  data = data,
  strata=c("name"),
  test = F), 
  showAllLevels=F,
  smd=T,
  nonnormal = vars, #all 
  noSpaces = TRUE,
  printToggle=FALSE)

for(i in 1:2) {
# tidy up 
  cur_column <- summary.characteristics.confirmed[, i]
  cur_column <- str_extract(cur_column, '[0-9.]+\\b') %>% 
                as.numeric() 
  cur_column <-nice.num(cur_column)
  # add back in
 summary.characteristics.confirmed[, i] <- str_replace(string=summary.characteristics.confirmed[, i],
                              pattern='[0-9.]+\\b', 
                              replacement=cur_column)    
}

@@

```{r include=FALSE}

data <- m.first_infection_reinfections[[3]]

summary.characteristics.reinfections<-print(svyCreateTableOne(
  vars =  vars,
  factorVars = factor.vars,
  includeNA=F,
  data = data,
  strata=c("name"),
  test = F), 
  showAllLevels=F,
  smd=T,
  nonnormal = vars, #all 
  noSpaces = TRUE,
  printToggle=FALSE)

for(i in 1:2) {
# tidy up 
  cur_column <- summary.characteristics.reinfections[, i]
  cur_column <- str_extract(cur_column, '[0-9.]+\\b') %>% 
                as.numeric() 
  cur_column <-nice.num(cur_column)
  # add back in
 summary.characteristics.reinfections[, i] <- str_replace(string=summary.characteristics.reinfections[, i],
                              pattern='[0-9.]+\\b', 
                              replacement=cur_column)    
}

@@

summary.characteristics_symptoms <-print(svyCreateTableOne(
  vars =  vars,
  factorVars = factor.vars,
  includeNA=F,
  data = s.data,
  strata=c("name"),
  test = F), 
  showAllLevels=F,
  smd=T,
  nonnormal = vars, #all 
  noSpaces = TRUE,
  printToggle=FALSE)

for(i in 1:2) {
# tidy up 
  cur_column <- summary.characteristics_symptoms[, i]
  cur_column <- str_extract(cur_column, '[0-9.]+\\b') %>% 
                as.numeric() 
  cur_column <-nice.num(cur_column)
  # add back in
summary.characteristics_symptoms[, i] <- str_replace(string=summary.characteristics_symptoms[, i],
                              pattern='[0-9.]+\\b', 
                              replacement=cur_column)    
}

@@

summary.characteristics_symptoms <-print(svyCreateTableOne(
  vars =  vars,
  factorVars = factor.vars,
  includeNA=F,
  data = s.data,
  strata=c("name"),
  test = F), 
  showAllLevels=F,
  smd=T,
  nonnormal = vars, #all 
  noSpaces = TRUE,
  printToggle=FALSE)

for(i in 1:2) {
# tidy up 
  cur_column <- summary.characteristics_symptoms[, i]
  cur_column <- str_extract(cur_column, '[0-9.]+\\b') %>% 
                as.numeric() 
  cur_column <-nice.num(cur_column)
  # add back in
summary.characteristics_symptoms[, i] <- str_replace(string=summary.characteristics_symptoms[, i],
                              pattern='[0-9.]+\\b', 
                              replacement=cur_column)    
}
